Accuracy Analysis For Three Mechanisms

### 2019-02-25 notes/AccuracyAnalysis/main.tex
rename and update the notes for Lapalce mechanism optimal analysis

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}

\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \citet{dimitrakakis2014robust}, and
\citet{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \citet{zhang2016differential}, \citet{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

When the output of a differentially private mechanism is a probability
distribution, accuracy is naturally measured by means of
\emph{probabilistic distances} measuring how far this distribution is
from the original one. Some classical examples are total variation distance,
Hellinger distance, $\chi^2$-distance, KL-divergence, etc.

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-Multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with an approach based on
the Laplace mechanism.
\end{abstract}

% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
% \begin{CCSXML}
% <ccs2012>
% <concept>
% <concept_id>10002978.10003029.10011703</concept_id>
% <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
% <concept_significance>500</concept_significance>
% </concept>
% </ccs2012>
% \end{CCSXML}

% \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% % -- end of section to replace with generated code

\keywords{Differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords

@@

\section{An informal motivation}
\label{sec_intro}
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to  introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.

\section{Bayesian Inference Background}
\label{sec_background}
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is computed as:
\[
  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression $\Pr(\dataobs | \theta)$ denotes the
\emph{likelihood} of observing $\dataobs$ under a value of
$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distributions. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior
simplifies calculations and allows for inference to be performed in a
recursive fashion over the data.
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
Specifically, we will consider the situation where $\theta$ represents
the parameter --informally called \emph{bias}-- of a Bernoulli
distributed random variable, and its immediate generalization where
the parameter $\vtheta$ represents the vector of parameters of a
categorically distributed random variable.  In the former case, the
prior distribution over $\theta\in [0,1]$ is going to be a beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:

\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
From this it can easily be derived that the posterior distribution is:
\[
  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)
\]
In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the componentwise sum of vectors of reals.

\section{The Problem Statement}
\label{sec:base}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$,
and where $Lap(\mu,\nu)$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$.
Our choice to use Hellinger distance is motivated by two facts, first of all it simplifies
calculations in the case of the probabilistic models considered here
and second of all it also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.

@@

% We use probability proportional to $exp(\frac{\epsilon u(x,r)}{\Delta_{g}u})$ rather than $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$. Since $\hlg$ is monotonic, i.e. our utility function is monotonic.

% \subsubsection{Security Analysis}
% It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
% \begin{equation*}
% \begin{split}
% \frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
% & =\frac
% {\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
% {\frac
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% {\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
% & = \left(\frac
% {exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
% {exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp\left(\frac
% {\epsilon (u(x,r) - u(y,r))}
% {2 \Delta_{g}u}
% \right)
% \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & \leq
% exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
% \left(\frac
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% {\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
% \right)\\
% & = exp(\epsilon).
% \end{split}
% \end{equation*}

% Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}$ share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
\end{equation*}

@@

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

\end{lem}

\begin{proof}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:

$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$

To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
\begin{equation*}
\begin{split}
LHS 
  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
\end{split}
\end{equation*}

By bounding the $\Delta \geq -S(x)$, we can get:

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
\end{split}
\end{equation*}

\end{proof}

\subsubsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

\begin{proof}

The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\

\textbf{Detail proof:}

	By simplification, we get this formula: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$
\begin{itemize}
	\item $\lambda < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
\begin{equation*}
u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
\end{equation*}
By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
\begin{equation*}
\begin{split}
Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
\end{split}
\end{equation*}

In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
\begin{equation*}
\begin{split}
Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
\end{split}
\end{equation*}

When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.

\end{proof}

\subsubsection{Privacy Analysis}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

\begin{proof}
of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
\end{equation*}
Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
\end{split}
\end{equation*}

The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

\end{proof}

@@

% where $m$ is the order of the Dirichlet distribution. Then we have the accuracy bound based on $\hlg$ distance.
% \begin{equation*}
% \begin{split}
% Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_1 \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}] & \leq Pr[m ||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq m \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = Pr[||Lap(\bysinfer(x)) - \bysinfer(x)||_{\infty} \geq \ln (\frac{m}{\gamma}) \frac{2}{\epsilon}]\\
% & = \gamma
% \end{split} 
% \end{equation*}

\subsection{Exponential Mechanism with Global Sensitivity}
\label{subsec_accuracy_global}
Also, according to \cite{dwork2014algorithmic}, we already had the accuracy bound of exponential mechanism with global sensitivity as:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq  \frac{|R| \exp{(\frac{- \epsilon c}{2 \Delta_g}})}{|R_{OPT}|\exp{(\frac{- \epsilon OPT_{\hlg(\bysinfer(x), z)}(x)}{2 \Delta_g})}},
\end{equation*}
where $|R|$ is the size of the candidate set. Since $OPT_{\hlg(\bysinfer(x), z)}(x) = 0$ and $|R_{OPT}| = 1$, we simplified accuracy bound here $\underset{z \thicksim \hexpmech(x)}{Pr}[ \hlg(\bysinfer(x), z) \geq c] \leq |R| \exp{(\frac{- \epsilon c}{2 \Delta_g}}),$

@@

Within the three accuracy bounds, we will mainly use the first one in following analysis.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

\section{Experimental Evaluations}
\label{sec_experiment}

\subsection{Computation Efficiency}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hlg(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always happen when $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(x), \bysinfer(x)) - \hlg(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hlg(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}
In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs. In all the experiments we set
$\epsilon = 0.8$, and $\delta = 10^{-8}$.

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents our newly
designed exponential mechanism's behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the yellow box next to
it represents the performance of a variation of the basic Laplace
mechanism presented in Section (\ref{sec:base}) with the same
settings: that is $\epsilon, \delta$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[Data set size from $300$ to $800$ ]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_800.eps}
    \label{subsubsec_vs_datasize1a}
  }
  \subfigure[Data set size from $14000$ to $20000$]{
    \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_20000.eps}
  \label{subsubsec_vs_datasize1b}} 
\caption{Increasing data size with fixed prior $\betad(1,1)$. Unbalanced datasets of mean $(0.1,0.9)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
  % \subfigure[Data set size from $300$ to $800$ ]{
  %   \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_300_dirichlet.eps}
  %   \label{subsubsec_vs_datasize1adir}
  % }
  \subfigure[Data set size from $14000$ to $20000$]{
     \includegraphics[width=0.45\textwidth]{accuracy_vs_datasize_1k_dirichlet.eps}   
  \label{subsubsec_vs_datasize1bdir}
  } 
\caption{Increasing data size with fixed $\dirichlet(1,1,1)$ prior distribution, Unbalanced datasets of mean $(0.2,0.3, 0.5)$ and parameters $\epsilon = 0.8$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_dir}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize} and \ref{fig_vs_datasize_dir} we consider \emph{unbalanced} datasets
of observations. This means that in the Beta-Binomial setting (Figure \ref{subsubsec_vs_datasize1a},
and \ref{subsubsec_vs_datasize1b}) the datasets will consist of 10\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})
the data will be split in the $k=3$ bins with perecentages of: 20\%, 30\% and 50\%.
The results show that when the data size
increases, the average errors of
$\hexpmech$, $\hexpmechd$, and Laplace decrease. For small datasets,
i.e with size less 650 in the case of Beta-Binomial systems,
the Laplace mechanisms outperforms the exponential mechanisms,
but for bigger data sets, that is, bigger than 650, or as in Figure \ref{subsubsec_vs_datasize1b} where
we considered data sets of the order of 15 thousands elements,
the exponential mechanisms outperforms the Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-Multinomial system ( (Figure  \ref{subsubsec_vs_datasize1adir} and \ref{subsubsec_vs_datasize1bdir})),
but we were not able to perform experiments with higher dimensions (4 or more) or, big datasets, e.g. $10^4$ elements, due to
too high run time of the algorithm.

>>>>

\begin{document}
\title{Accuracy Analysis For Three Mechanisms}

\begin{abstract} 
\end{abstract}

\keywords{Accuracy analysis} % TODO: replace with your keywords

@@

\section{Introduction}
\label{sec_intro}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(x)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(x)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(x)})},
\end{equation*}

@@

@@

\subsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal results.

@@

Moreover, based on the accuracy bound in Sec. \ref{subsec_accuracy_global}, we can derive a loose bound:

\begin{equation*}
\begin{split}
Pr[u(\hexpmech(x)) \leq c] 
& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)}),
\end{split}
\end{equation*}

which has been used in the dilation property proof.

@@
